---
title: "FastTrack Auction Scraper"
author: "Beaver Brigade Research & Innovation (BBRI)"
output:
  html_document:
    highlight: tango
    theme: journal
---
******

#### Getting a list of auctions
First we scrape the front page to learn what auctions are live. 
The tag for each auction container is `.auction`
```{r Dependencies, echo=F, message=F}
library(rvest)
library(dplyr)
library(knitr)
library(data.table)
library(rjson)
curtime  <- Sys.time()
```

We'll need to define some helpful functions for cleaning strings
```{r Helper Functions}
clean_str <- function(str) {
  str %>%
    gsub("[\t\n\r\v\f]", " ", .) %>%
    gsub(" +"," ",.) %>%
    gsub("^\\s+|\\s+$", "", .)
  }
```


```{r Top Level Auction Links}
link  <- html("http://bidfta.com/") %>%
  html_nodes(".auction")  %>% 
  html_node("a") %>%
  html_attr("href")

fix_these  <- grep("mnlist",link)

link[fix_these] <- link[fix_these] %>%
  gsub("mnlist","mndetails",.) %>%
  sub("/category/ALL","",.)
```


We create a function that traverses an auction link node to get the specific auction details we need
```{r Auction List & Details Scraper Function}
auction_details  <- function(link) {
  a  <- list()
  
  tmp <- html(link) %>%
    html_nodes("table tr td")
  
  a$date  <- tmp[[6]] %>% 
    html_text %>%
    gsub("st|nd|rd|th","", .) %>%
    gsub("\\.", ",", .) %>%
    strptime("%B %e, %Y %R")
  
  if (is.null(a$date) | a$date < curtime) return(NULL)
  
  a$title  <- tmp %>% 
    html_nodes("#auction_title") %>%
    .[[1]] %>% 
    html_text
  
  a$location  <- tmp[[8]] %>% html_text
    
  a$link  <- link %>%
    gsub("mndetails","mnlist",.) %>%
    paste0("/category/ALL")
  a
  }

```

Now we can traverse all the nodes to get all the auction details. We'll throw out auctions that have already expired.
```{r}
  auctions <- link[40:50] %>%
    lapply(auction_details) %>%
    .[!sapply(.,is.null)]
  
  auctions_df <- auctions %>% 
    lapply(data.frame, stringsAsFactors=FALSE) %>%
    do.call(rbind, .)
```


Here's what we scraped:
```{r}
auctions_df %>%
  kable
```

#### Filtering
It'll probably take a while to download all the item lists, so we'll filter out auctions not on the approved list.
```{r}
# Good locations
good_loc  <- c("Cincinnati", "Sharonville", "West Chester") %>% 
  sapply(function(x) grepl(x, auctions_df$location, ignore.case = T)) %>%
  apply(1, any)

auctions_df <- filter(auctions_df, good_loc)
```

#### Getting the auction itemlists
```{r Auction Itemlists}
get_itemlist  <- function(lnk){
  tmp <- html(lnk) %>%
    html_node("#DataTable")
  
  img_src  <-  tmp  %>%
    html_node("img") %>%
    html_attr("src") %>%
    gsub("\\/\\w+\\.(jpg|jpeg|png)","",.)
  
  tmp %>%
    html_table(header = T) %>%
    mutate(Description = iconv(Description, to='UTF-8-MAC', sub = '')) %>%
    mutate(img_src = paste0(img_src, "/", Item)) %>%
    mutate(link = lnk  %>% gsub("category/ALL","", .) %>% paste0(Item)) %>%
    select(-contains("Photo"))
  
} 

# tmp <- auctions_df$link[151] %>%
#   lapply(get_itemlist)

items <- auctions_df$link %>%
  lapply(get_itemlist)

names(items) <- auctions_df$title

items_df <- items %>%
  do.call(rbind, .) %>%
  mutate(Auction = gsub("\\.[0-9]+","", row.names(.)))

```

#### Search
```{r}
phrase  <- "florentine"

# # Search for `list` object
# found <- items %>% 
#   lapply(function(x) grep(phrase, x$Description, value = T, ignore.case = T)) %>%
#   .[ sapply(., length) > 0 ]

# Search for `data frame` object
found <- items_df$Description %>% 
  grep(phrase, ., value = F, ignore.case = T) %>%
  items_df[.,] %>%
  mutate(Photo = paste0('<a href = "', link ,'"><img src="',img_src, '"></a>'))

found
```

