---
title: "Summarizing Auctions & Items on Fast-Track"
people: "and stuff"
author: "Eugene"
date: "`r format(Sys.time(), '%B %e, %Y')`"
output:
  html_document: 
    css: ~/Ahalogy/R/style.css
    highlight: tango
    theme: null
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache=T, fig.width=6.5, fig.height=6.5, 
                      fig.path='Figs/', warning=FALSE, message=FALSE)
```

***
## Getting things set up
```{r Parameters}
OS.Name <- Sys.info()["sysname"]
numcores <- parallel::detectCores()
TOKENIZER_TM = 1 #default tokenizer in TM package
TOKENIZER_BIGRAM = 2 #bigram tokenizer in RWEKA package
tokenizer = TOKENIZER_TM

BigramTokenizer <- function(x) {RWeka::NGramTokenizer(x, RWeka::Weka_control(min = 1, max = 2))}
```

```{r Initialization}
require(dplyr)
require(ggplot2)
require(knitr)
require(tm)
library(stringr)
library(topicmodels)
library(wordcloud)
library(data.table)
library(tagcloud)
source("~/Google Drive/Ahalogist Toolkit/R/theme_ahalogy.R")
attach(ahalogy.colors)

# Stopwords removal
all.stopwords <- read.csv("stopwords_bidfta.csv", header = F, stringsAsFactors = F) %>%
    unlist %>%
    # gsub(" ","",.) %>%
    union(stopwords()) #%>% 
    # union(c("description", "item", "new", "contact", "appears", "condition", "preview", "newitem"))

```

We read in a flat file of a few thousand item descriptions
```{r Reading Data}
descriptions <- fread("CSV/items.csv") %>% .[["Description"]]
length(descriptions)
```

The descriptions need some cleaning and preprocessing before we can assemble them into a `term-document matrix`
```{r Cleaning & Term Document}
# Fix descriptions and make Corpus
rm_pattern <- c("Facebook", "Twitter", "Pinterest", "Load #", "Lotted") %>% 
    paste0( "\\W\\w*", . , "\\w*(\\W|$)", collapse = "|" ) %>% 
    paste0( "|Front Page: Click here to go back to Fast Track Auction Home Page" ) %>% 
    paste0( "|Contact: Please use our contact submission via bidfta.com to submit any questions regarding this auction.") %>% 
    paste0( "|[Ii]tem" )

descriptions <- descriptions %>% 
    str_replace_all("[^[:graph:]]", " ") %>% 
    gsub(rm_pattern, " " , .,  perl = T, ignore.case = FALSE)
    

myCorpus <- Corpus(VectorSource(descriptions)) %>% 
    tm_map(content_transformer(tolower)) %>% 
    tm_map(removePunctuation) %>% 
    tm_map(removeNumbers) %>% 
    tm_map(removeWords, all.stopwords)
```

## Keyword Extraction
```{r Keywords}
# Tokenizing the documents and creating a Term-Document Matrix
if (tokenizer == TOKENIZER_TM) {
    tdm <- myCorpus %>% TermDocumentMatrix } else if (tokenizer == TOKENIZER_BIGRAM) {
    # Have to set cores = 1 because Weka blows
    options(mc.cores = 1)
    tdm <- myCorpus %>%
        TermDocumentMatrix(control = list(tokenize = BigramTokenizer))
}

```

```{r}
# Remove sparse terms
tdm <- tdm %>% 
    weightTfIdf %>% 
    removeSparseTerms(.999)
tdm
```

We've removed __sparse__ terms (i.e. those that occur in just a tiny percentage of documents), and here's what's left.
```{r Frequent Terms}
term.freq <- rowSums(as.matrix(tdm)) %>% 
    sort(decreasing= T)
term.freq %>% data.frame %>% head(50)
```


### RELEVANT WORDS FOR ONE DOC
```{r}
get_terms <- function(tdm_col, num_terms=5) {
    selected <- tdm_col %>% as.matrix %>% 
        order(decreasing=T) %>% 
        head(num_terms)
        
   tdm_col[selected,] %>% 
       as.matrix %>% 
       data.frame(val = as.numeric(.)) %>% 
       add_rownames("terms") %>% 
       select(terms, val)
}

tdm[,5] %>% get_terms
```


### Word Cloud
```{r Tagcloud function, echo = FALSE}
outputTagcloud <- function(term.freq, cloud_terms) {
  
  #font.vec  <- paste0("Helvetica Neue",c(" Bold", " Medium", "", " Light", " Thin"))
  font.vec  <- c("FuturaLT-Bold", rep("FuturaLT-Book", 4))
  
  if (length(term.freq) > cloud_terms) {
    term.freq <- term.freq[1:cloud_terms]
    }
  
  bucket  <- ntile(-sqrt(term.freq), 5)
  
  tagcloud(names(term.freq), term.freq, 
    algorithm = "fill",
    scale.multiplier = 1.35,
    family = font.vec[bucket], 
    fvert= 0.3,
    col = blue_light
    #col = smoothPalette( term.freq, pal= "Blues", n = 3)
    )
  }
```

```{r Plot Tagcloud}
outputTagcloud(term.freq, 200)
```


## Topic Modeling
Now we run Latent Direchlet Allocation (`LDA`) to associate every description with one or more topics. This method requires us to choose the __total__ number of topics ahead of time.
```{r LDA}
#Number of topics
k <- 30

#Set parameters for Gibbs sampling
alpha <- .1
verbose <- 250
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

dtm <- as.DocumentTermMatrix(tdm)
empty.docs  <- (rowSums(as.matrix(dtm)) == 0)
table(empty.docs)
dtm <- dtm[rowSums(as.matrix(dtm)) != 0,]
    
ptm <- proc.time()
cat("Running LDA for", k, "topics ... ")
LDA.output <- LDA(dtm, k, method = "Gibbs", 
                  control=list(nstart = nstart, seed = seed, best = best, 
                               burnin = burnin, iter = iter, thin=thin,
                               verbose = verbose, alpha = alpha))
cat((proc.time() - ptm)[["elapsed"]],"seconds\n")
```

The output of this LDA model contains a bunch of stuff, including the assignment of descriptions to topics (function `topics`), the probabilistic interpretation of a topic as a collection of underlying terms (function `terms`), 

Let's look at how the algorithm allocates our pin descriptions among the 30 topics. In effect, this is _clustering_.

### LDA: Allocation of pin descriptions by Topic
```{r Topics}
topics <- LDA.output %>% topics
table(topics)
qplot(topics, binwidth = 1) + 
    theme_ahalogy() +
    scale_x_discrete(limits = c(1:k)) +
    xlab("Topic ID") + ylab("Count of Descriptions in Topic")
```


### Top 6 Terms for Each topic

```{r kable Splitter, echo = F}
kable_split <- function(df, newcols = 5) {
    
    groups <- ncol(df) / newcols
    for (i in (1:groups) * newcols) {
        df[,(i-newcols + 1):i] %>% kable %>% print
    }
}
```


```{r}
terms <- LDA.output %>% terms(10)
kable_split(terms, 5)
```


### Probabilities Associated with Each Topic Assignment per doc

Here is the distribution for the first 30 documents
```{r}
gamma <- LDA.output@gamma %>% data.frame
gamma %>% head(30)%>% round(3)

LDA.output@gamma  %>% head(30) %>% t %>% barplot
#LDA.output@gamma  %>% head(30) %>% rowSums()
```


```{r}
gamma2 <- gamma %>% cbind(doc = rownames(.),  .) %>% head(50)%>% melt 

ggplot(gamma2, aes(x = factor(doc, levels = paste0(1:50)), y = value, fill = variable))+
    geom_bar(stat = "identity", position = "stack") +
    labs(title = "Composition of Documents by Topic", 
         x = "Document #",
         y = "% by Topic") +
    coord_flip() + scale_fill_brewer(palette = "Set3")
```

